A thesis draft

### 2018-11-26 res/sections/15-ArchitecturalImplementation.tex
Add something

After the failure to find a viable setting for Openstack, we decided to look
around for other solutions. We started studing proper Docker container
orchestrators, that could offer all the features we needed: container lifecycle
management, scaling, healing and monitoring. We decided to pick two of the most
mature and famous ones: Docker Swarm and Kubenetes. The decision to study only
these two relies on their big community supporting them and the possibility to
easily found projects that used the forementioned frameworks.

@@

\subsection{Kubernetes}

>>>>

After the failure to find a viable setting for Openstack, we decided to look
around for other solutions. We started studing proper Docker container
orchestrators that could offer all the features we needed: container lifecycle
management, scaling, healing and monitoring. We decided to pick two of the most
mature and famous ones: Docker Swarm and Kubenetes. The decision to study only
these two relies on their big community supporting them and the possibility to
easily found projects that used the forementioned frameworks.

@@

\subsection{Kubernetes}
Kubenetes, as already described in the technology section, is a orchestrator 
created by Google able to create a software abstraction from the underlying 
virtualization technology. This enables Kubernetes to create an integration 
with the Docker technology. Kubernetes has a architecture based on plug-ins, 
giving  the possibility to the users to change part of Kubernetes itself, such 
as the networking routing strategy or the persistence layer. With this 
flexibility Kubernetes offered to us what Docker Swarm was not able to give. 
Additionally, we had the possibility to set custom Domain Name System (DNS) 
lookups and distribute other internal components in order to avoid requests 
bottleneck.

\subsection{Kubernetes configuration}
Kubernetes does not have a minimum number of nodes in order to properly 
function. Nonetheless, we decided to use a four node cluster configured in the 
following way: three slaves node (also known as \emph{minions}) and one master 
node. The Kubernetes version installed was the 1.11, enabling us to exploit new 
features like a reworked DNS lookup system, a better intergrated\todo{find our 
1.11 new features}.
